The complex network of trophic interactions in a subAntarctic Marine Protected

### 2023-02-01 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue Discussion

Food web connectance is a property that resumes the complexity of the network. It contains important information regarding how interactions within an ecological network are distributed, and predicts reasonably well key dynamical properties of ecological networks  also many structural [@Dunne2002a]. More importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
Complex marine food webs (i.e. with more than 25 trophic species) show connectance values ranging from 0.01 - 0.27 [@Marina2018a]. In particular, food webs from high-latitude regions tend to exhibit a connectance closer to the minimum (between 0.01 and 0.05) [@Santana2013; @Kortsch2015; @Rodriguez2022]. Whether food webs display low or high connectance values helps to better comprehend ecosystem's synthetic properties like robustness. In this sense, empirical analyses support the notion that the robustness of a food web increases with connectance [@Dunne2002; @Montoya2003]. The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; five times lower than that of Beagle Channel [@Rodriguez2022].

The degree distribution or the distribution of number of interactions per species is the core for the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018]. The food web for the MPA N-BB presents an asymmetric degree (interaction) distribution. This is a pattern that we have identified at different levels of analysis: food web, predator, prey, and functional group. Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing a catastrophic fragmentation of the network [@Albert2000; @Dunne2002].

Small-world
The path length, another network-level property we analysed, refers to the average shortest distance between pairs of species in the food web. A short path length implies a rapid spread of an impact (e.g. contaminant, population fluctuation, local extinction) throughout the network [@Williams2002]. In comparison to complex and empirical marine food webs, the food web of the MPA Namuncurá - Banco Burdwood has a long path length (4th longest among 29 food webs) [@Marina2018a].

>>>>

Food web connectance is a feature that resumes the complexity of the network, but more importantly it is an emergent property of pairwise species interactions [@Poisot2014]. It contains information regarding how interactions within an ecological network are distributed, and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
Complex marine food webs (i.e. with more than 25 trophic species) show connectance values ranging from 0.01 - 0.27 [@Marina2018a]. In particular, food webs from high-latitude regions tend to exhibit a connectance closer to the minimum (between 0.01 and 0.05) [@Santana2013; @Kortsch2015; @Rodriguez2022]. Whether food webs display a low or a high connectance helps to better comprehend ecosystem's synthetic properties like robustness. In this sense, empirical analyses support the notion that the robustness of a food web increases with connectance [@Dunne2002; @Montoya2003]. The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; five times lower than that of Beagle Channel [@Rodriguez2022].

The degree distribution or the distribution of number of interactions per species is the core for the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018]. The food web for the MPA N-BB presents an asymmetric degree (interaction) distribution. This is a pattern that we have identified at different levels of analysis: food web, predator, prey, and functional group. Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].

The small-world pattern is a property that has implications for network functioning [@Strogatz2001].

The path length, another network-level property we analysed, refers to the average shortest distance between pairs of species in the food web. A short path length implies a rapid spread of an impact (e.g. contaminant, population fluctuation, local extinction) throughout the network [@Williams2002]. In comparison to complex and empirical marine food webs, the food web of the MPA Namuncurá - Banco Burdwood has a long path length (4th longest among 29 food webs) [@Marina2018a].
